---
title: "Steam Exploration"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Get the data

We'll use the Steam Spy API to get the dataset of all games on Steam and the estimated number of owners for each game.  This site doesn't have a published API client, so we just need to call the data directly. 

### Pull data for a single entry
This is the data for Counter-Strike: Global Offensive

```{r}
library(httr)
spy_url <-"http://steamspy.com/api.php?request=appdetails&appid=730"
single_game <- content(GET(url = spy_url))
```

### Pull the list of all games

```{r, eval = FALSE}
spy_games <- "http://steamspy.com/api.php?request=all"
game_list <- content(GET(url = spy_games))
print(object.size(game_list), units = "Mb")
saveRDS(game_list, file = "game_list.RDS")
```

## Create unique links for each game to get app details

# Initial Visualization

We'll take a preliminary look at the relationship between reviews and number of owners. 

```{r, echo=FALSE}
```

